Preprocessing overview

### 2021-02-11 inst/examples/corporate.Rmd

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$corporate))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/corporate_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$corporate))` / `r nrow(df)` (`r round(100*mean(!is.na(df$corporate)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$corporate)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$corporate)), 1)`%)

>>>>

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$corporate))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/corporate_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$corporate))` / `r nrow(df)` (`r round(100*mean(!is.na(df$corporate)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$corporate))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$corporate)), 1)`%)

### 2021-02-11 inst/examples/details.Rmd

---
title: "Details"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

>>>>

---
title: "Preprocessing details"
author: "`r author`"
date: "`r Sys.Date()`"
output: markdown_document
---

## Annotated documents

Fraction of documents with data:

```{r summaryannotations, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=8, fig.height=11}
availability <- field_availability(df)
print(availability$plot)
```

Same in exact numbers: documents with available/missing entries, and number of unique entries for each field. Sorted by missing data:

```{r sumtab, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
tab <- availability$table %<>% arrange(n)
names(tab) <- gsub("missing", "missing (%)", names(tab))
names(tab) <- gsub("available", "available (%)", names(tab))
names(tab) <- gsub("^n$", "available (n)", names(tab))
names(tab) <- gsub("unique_entries", "unique (n)", names(tab))
names(tab) <- gsub("field_name", "field name", names(tab))
kable(tab[, c(1, 3, 2, 4, 5)], digits = 1, caption = "Data availability")
rm(tab);gc()
```

## Field conversions

This documents the conversions from raw data to the final preprocessed version (accepted, discarded, conversions). Only some of the key tables are explicitly linked below. The complete list of all summary tables is [here](output.tables/).

Brief description of the fields:

 * [Description of the original MARC fields](https://github.com/COMHIS/fennica/blob/master/inst/extdata/fieldnames.csv)

 * [Description of the preprocessed fields](https://github.com/COMHIS/fennica/blob/master/inst/extdata/fieldname_table.csv)

## Histograms of all entries for numeric variables

```{r summary-histograms, echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=4, fig.show='hold', out.width="200px"}
num <- c();
for (field in names(df)) {num[[field]] <- is.numeric(df[[field]])}
numeric.fields <- setdiff(names(which(num)), c("row.index", "original_row", "unity"))
for (field in numeric.fields) {
  x <- log10(min(df[[field]], na.rm = TRUE)/2 + df[[field]])
  x <- x[!is.na(x) & !is.nan(x)]
  if (length(x) > 0) {
    hist(x, 30,
       main = paste(field, "histogram"),
       ylab = "Documents",
       xlab = paste(field, "(log10)")
       )
  }
}
```

## Histograms of the top entries for factor variables

Non-trivial factors with at least 2 levels are shown.

```{r summary-bars, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=5, fig.show='hold', out.width="430px"}
fac <- c(); for (field in names(df)) {fac[[field]] <- is.factor(df[[field]])}
factor.fields <- names(which(fac))
for (field in factor.fields) {
  n <- min(length(unique(df[[field]])), ntop)
  if (length(n) > 1) {
    p <- top_plot(df, field, n)  
    p <- p + ggtitle(paste("Top ", field))
    p <- p + scale_y_log10()
    p <- p + ylab("Documents (Log10)")
    print(p)
  }
}
```

Fields of special interest. Real success percentage (proportion of successful conversions compared to non-NA entries in the original data):

```{r missing2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
select.fields <- c("author","publication_place","publication_country","publication_year",
                     "publication_year_from","publication_year_till","corporate","area","pagecount",
		     "gatherings","width","height","publisher","self_published")

dfs <- df

success <- as.data.frame(t(apply(dfs, 2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))

original.nonNA <- as.data.frame(t(apply(select(df.orig, publication_place,
                    publication_time, corporate, physical_extent, physical_dimension, publisher, author_name),
		      2, function (x) {sum(!is.na(gsub("^NA$", NA, as.character(x))))})))

# Compare the number of non-NA entries in preprocessed data to number
# of non-NA entries in the original data:
real.success <- c()
real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
real.success[["publication_country"]] <- success$publication_country/original.nonNA$publication_place
real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
real.success[["publication_year_from"]] <- success$publication_year_from/original.nonNA$publication_time
real.success[["publication_year_till"]] <- success$publication_year_till/original.nonNA$publication_time
real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
real.success[["area"]] <- success$area/original.nonNA$physical_dimension
real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
real.success[["author"]] <- success$author/original.nonNA$author
# real.success[["paper"]] <- success$paper/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
real.success <- unlist(real.success)
par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
```

### 2021-02-11 inst/examples/note_dissertation.Rmd

---
title: "note_dissertation"
output: md_document
---
 * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_dissertation))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_dissertation_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$note_dissertation))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_dissertation)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$note_dissertation))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_dissertation)), 1)`%)

>>>>

---
title: "note_dissertation"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

 * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_dissertation))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_dissertation_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$note_dissertation))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_dissertation)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$note_dissertation))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_dissertation)), 1)`%)

### 2021-02-11 inst/examples/note_source.Rmd

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_source)`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_source_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$note_source))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_source)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$note_source))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_source)), 1)`%)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_source))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_source_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$note_source))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_source)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$note_source))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_source)), 1)`%)

### 2021-02-11 inst/examples/overview.Rmd

  * [Author info](author.md)
  * [Gender info](gender.md)
  * [Publisher info](publisher.md)
  * [Publication geography](publicationplace.md)
  * [Publication year info](publicationyear.md)
  * [Titles](title.md)  
  * [Page counts](pagecount.md)
  * [Physical dimension](dimension.md)    
  * [Document and subject topics](topic.md)
  * [Languages](language.md)

See also [further preprocessing details](details.Rmd).

>>>>

  * [Author info](author.md)
  * [Gender info](gender.md)
  * [Publisher info](publisher.md)
  * [Publication geography](publicationplace.md)
  * [Publication year info](publicationyear.md)
  * [Titles](title.md)  
  * [Page counts](pagecount.md)
  * [Physical dimension](dimension.md)    
  * [Document and subject topics](topic.md)
  * [Languages](language.md)
  * [Corporate](corporate.md)
  * [Holder](holder.md)
  * [Note_510c](note_510c.md)
  * [Note_dissertation](note_dissertation.md)
  * [Note_granter](note_granter.md)
  * [Note_source](note_source.md)
  * [Subject_topic](subject_topic.md)
  * [Successor](successor.md)
  * [Title_uniform](title_uniform.md)
  * [Uncontrolled](uncontrolled.md)
See also [further preprocessing details](details.Rmd).
